\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-03 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

Notice that the proximal recursions given by \eqref{InfiniteDimProxOpDef}-\eqref{ProxRecursionInfiniteDim} define an infinite dimensional gradient descent of the functional $h\Phi$ over $\mathcal{P}_{2}$ w.r.t. the distance ${\rm{dist}}$. This is reminiscent of the finite dimensional gradient descent, where a gradient flow generated by an ordinary differential equation initial value problem can be recovered as the small time step limit of the sequence of vectors generated by a standard Euclidean proximal recursion; see e.g., \cite[Sec. I]{caluya2019TAC}.

>>>>

We can interpret the proximal operator \eqref{InfiniteDimProxOpDef} as a generalized gradient step for the functional $\Phi$ in the manifold $\mathcal{P}_{2}$. The proximal recursions \eqref{ProxRecursionInfiniteDim} define an infinite dimensional gradient descent of the functional $h\Phi$ over $\mathcal{P}_{2}$ w.r.t. the distance ${\rm{dist}}$. This is reminiscent of the finite dimensional gradient descent, where a gradient flow generated by an ordinary differential equation initial value problem can be recovered as the small time step limit of the sequence of vectors generated by a standard Euclidean proximal recursion; see e.g., \cite[Sec. I]{caluya2019TAC}.
